---
title: "COVID-19 crime data"
output: html_notebook
---

I am going to merge all of the data together so I can analyse whether crime rates have increased during covid-19 despite there being less people taken into prisons.

As there are a lot of csvs to organise and sort through, I am instead going to try out this code from stackoverflow. 

```{r}
install.packages("dplyr")
install.packages("readr")
install.packages("plyr")

library("dplyr")
library("plyr")
library("readr")
```
This code is going to read all of the csvs in the folder which has 86 seperate csvs. 

Since they all have the same headings etc, I am going to attempt to merge this data afterwards. 


```{r}
data_all <- list.files(path = "covid data", 
                       pattern = "*.csv", full.names = TRUE)%>%
 
  lapply(read_csv) %>%                                          
  bind_rows                                                       
  data_all 
```

```{r}
as.data.frame(data_all)

head(data_all, n=10)
dim(data_all)

write.csv(data_all,"final/completedata.csv", col.names = FALSE)

```

Now that we have combined all of the data, I'm going to try and analyse some of this data so that I can get some information from it.

```{r}
data_all %>%
select('Outcome type')
summarise(data_all,)

```