---
title: "West Midlands crimes during lockdown compared to last year"
output: html_notebook
---

This R package is simply to merge all of the data together from the months March-June in 2020 and 2019, both in seperate years. From this I am going to attempt to see if there was a decline in arrests during the turn of lockdown and attempt to find out the reason for this. 

So first off we are going to install all the relevant packages we need and put them into our library.

```{r}
install.packages("dplyr")
install.packages("readr")
install.packages("plyr")

library("dplyr")
library("plyr")
library("readr")
```

Now we are going to begin by finding all of the files in the relevant folder so that R can merge them together. This is for the 2020 data.

We will then double check the data has the right amount of rows and columns, and then write the combined data into a CSV so that we can analyse it on Excel, as that is what we are more comfortable with! 

```{r}
data_all <- list.files(path = "westmidsdata",
                       pattern = "*csv", full.names = TRUE)%>%
  
  lapply(read_csv) %>%
  bind_rows

data_all

write.csv(data_all,"westmidsdata/compileddata.csv", row.names = FALSE)

```

We are now going to do exactly the same thing for our data in 2019, I'm not sure why I have done this a bit backwards but that is fine. We will get the data either way! 

I put all of the data into a seperate folder so that it keeps it easy for R and doesn't get too confusing. But we are essentially going to copy the code and change a few little bits, including where we are going to make R look and what we are going to call the final csv file.

We shall also call it a different variable so that it just makes more sense. We want to keep these as seperate as possible! 

```{r}
previous_data <- list.files(path = "westmidsdata2",
                       pattern = "*csv", full.names = TRUE)%>%
  
  lapply(read_csv) %>%
  bind_rows
```

Looking at the data environment to the top right (which you won't be able to see, but I can, muahahahaha), it already looks like there has been a decline in crimes in 2020 during the lockdown. 

```{r}
write.csv(previous_data,"westmidsdata2/compileddata.csv", row.names = FALSE)
```

Just so we can compare it even further, I am going to do the same with the 2018 data, so we can see whether 2019 was just a fluke... got to stay skeptical! 

```{r}
other_data <- list.files(path = "westmidsdata3",
                       pattern = "*csv", full.names = TRUE)%>%
  
  lapply(read_csv) %>%
  bind_rows
```

And it seems like it may have been a fluke as there was only 179,869 rows in this dataset... that puts a bit of a spanner in the works, but I'm still going to download the combined data so that I can compare it to 2019 and 2020. 

```{r}
write.csv(other_data,"westmidsdata3/combineddata.csv", row.names = FALSE)
```